---
title: "Diameter experiments"
output: html_document
---

```{r echo=FALSE}
knitr::opts_chunk$set(echo=FALSE)
```

### Diameter vs. time

Down and to the left is better.
When the auxiliary graph has a single node (happens when the radius parameter is too large) then we have to multiply the radius estimate by two, to continue an estimate upper bounding the radius.

```{r fig.width=8, fig.height=8}
readd(plot_interactive_diam_vs_time)
```

### Center selection by iteration

Note that in some configurations the number of centers
decreases with respect to the previous iteration, even though the probability
increases. This is due to the decrease in the number of uncovered nodes from
which we sample the centers.
Suppose that in one iteration the probability of selecting a center is 0.05 and there
are 5000 uncovered nodes: the expected number of centers will be 250.
If in the next iterations there are just 1000 uncovered nodes, and the probability
of selecting a center is 0.1, the expected number of centers will be 100.

```{r}
#readd(plot_centers_interactive)
```

### Uncovered nodes by iteration

```{r}
#readd(plot_uncovered_interactive)
```
